Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-09-16 supp/index.Rmd

Components of this analytical work flow were developed and funded by a Preservation Technology and Training grant (P14AP00138) to RZS from the National Center for Preservation Technology and Training (NCPTT), and additional grants to RZS from the Caddo Nation of Oklahoma, National Forests and Grasslands in Texas (15-PA-11081300-033) and the United States Forest Service (20-PA-11081300-074). Funding to analyse the bifaces from Millsap Cache and Jowell Farm was made possible by a Research Support Fund Grant from the Texas Archeological Society. Additional support for this project was provided by the Heritage Research Center at Stephen F. Austin State University.

>>>>

Components of this analytical work flow were developed and funded by a Preservation Technology and Training grant (P14AP00138) to RZS from the National Center for Preservation Technology and Training (NCPTT), and additional grants to RZS from the Caddo Nation of Oklahoma, National Forests and Grasslands in Texas (15-PA-11081300-033) and the United States Forest Service (20-PA-11081300-074). Funding to analyse the bifaces from Millsap Cache and Jowell Farm was made possible by support from the Heritage Research Center at Stephen F. Austin State University. A Research Support Fund Grant from the Texas Archeological Society provided the tool needed to illustrate the bifaces.
